Fixing Vulnerabilities Hinders Maintainability

### 2019-02-04 paper/ICPC19/icpc19.tex
more fixes

The dataset contains security flaws for more than $13$ different languages
being PHP ($39\%$) and C ($24\%$) the most prevalent ones; see Figure~\ref{fig:lang}.
To classify the applications in the dataset, we use a taxonomy for open-source
software from previous work~\cite{7816479}. Figure~\ref{fig:domain}
presents the projects domain distribution: \textit{Aplication Software} ($25$),
software that provides end-users with functional systems; \textit{Web libraries
and frameworks} ($20$); \textit{System Software} ($18$), software that provides
services and infrastructures (e.g., operating systems, servers and databases);
\textit{Software Tool} ($13$), software that supports development (e.g.,
programming languages, compilers, package managers, IDEs); and, \textit{Non-web
libraries and frameworks} ($18$), for desktop and mobile software.
%
Table~\ref{tab:dataset} presents the descriptive statistics of the $94$
open-source projects involved in this study, including the number of forks, the
number of stars, the number of watchers, the number of contributors, the number
of commits, the number of branches, the number of releases,  size (cf. GitHub it
is the size of the whole repository, including all of its history, in
kilobytes), the number of issues, and the number of pull requests.

>>>>

The dataset contains security flaws for more than $13$ different languages,
being PHP ($39\%$) and C ($24\%$) the most prevalent ones (see Figure~\ref{fig:lang}).
To classify the applications in the dataset, we use a taxonomy for open-source
software from previous work~\cite{7816479}. Figure~\ref{fig:domain}
presents the projects domain distribution: \textit{Aplication Software} ($25$),
software that provides end-users with functional systems; \textit{Web libraries
and frameworks} ($20$); \textit{System Software} ($18$), software that provides
services and infrastructures (e.g., operating systems, servers and databases);
\textit{Software Tool} ($13$), software that supports development (e.g.,
programming languages, compilers, package managers, IDEs); and, \textit{Non-web
libraries and frameworks} ($18$), for desktop and mobile software.
%
Table~\ref{tab:dataset} presents the descriptive statistics of the $94$
open-source projects involved in this study, including the number of forks, the
number of stars, the number of watchers, the number of contributors, the number
of commits, the number of branches, the number of releases,  size (cf. GitHub it
is the size of the whole repository, including all of its history, in
kilobytes), the number of issues, and the number of pull requests.
